Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: put_log1.

Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument using the format value specified by the [arg1](#func.put_log1.args.arg1).

@@

::: { #func.put_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.put_log1.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log1.args.msg_template) argument.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
:::

>>>>

Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument, using the value specified by the [arg1](#func.put_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.

@@

::: { #func.put_log1.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.put_log1.args.arg1) argument.

@@

::: { #func.put_log1.args.arg1 .sidebar }
  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.put_log1.args.msg_template) argument.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log1](#func.get_log1) function described above.

@@

A glue object, returned by the internally called function [get_log1](#func.get_log1) described above.
